\bf Eye Fitting Straight Lines in the Modern Era

### 2022-01-28 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
updated shinyapps.io link to new repository rsconnect

Participants were recruited through through Twitter, Reddit, and direct email in May 2021.
A total of 35 individuals completed 119 unique 'You Draw It' task plots; all completed you draw it task plots were included in the analysis. 
All participants had normal or corrected to normal vision and signed an informed consent form.
The experimental tasks took approximately 15 minutes to complete.
While this study does utilize a convenience sample, as this is primarily a perceptual task, previous results have found few differences between expert and non-expert participants in this context [@vanderplas2015spatial].
These data were collected to validate this method of graphical testing, with the hopes of providing a new tool to assess graphical perception interactively.
Participants completed the experiment on their own computers in an environment of their choosing. The experiment was conducted and distributed through a Shiny application [@shinyPkg] \ear{xxx added citation} found [here](https://emily-robinson.shinyapps.io/you-draw-it-pilot-app/). \svp{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?} \ear{XXX currently linked to my shinyapps.io page but will get this updated to a new repository.}

@@

+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be found [here](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).
+ **Study Applet:** The shiny app used to conduct the study can be accessed [here](https://emily-robinson.shinyapps.io/you-draw-it-pilot-app/).
+ **\ear{RShiny Applet Code:}** \ear{The code used to create the RShiny Applet for data collection can be found} [\ear{here}](https://github.com/earobinson95/you-draw-it-validation-applet).

>>>>

Participants were recruited through through Twitter, Reddit, and direct email in May 2021.
A total of 35 individuals completed 119 unique 'You Draw It' task plots; all completed you draw it task plots were included in the analysis. 
All participants had normal or corrected to normal vision and signed an informed consent form.
The experimental tasks took approximately 15 minutes to complete.
While this study does utilize a convenience sample, as this is primarily a perceptual task, previous results have found few differences between expert and non-expert participants in this context [@vanderplas2015spatial].
These data were collected to validate this method of graphical testing, with the hopes of providing a new tool to assess graphical perception interactively.
Participants completed the experiment on their own computers in an environment of their choosing. The experiment was conducted and distributed through a Shiny application [@shinyPkg] \ear{xxx added citation} found [here](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). \svp{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?} \ear{XXX linked to updated shinyapps.io through new repository - does not currently write data anywhere.}

@@

+ **Participant Data:** De-identified participant data collected in the study and used for analyses are available to be downloaded from GitHub [here](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data). 
+ **Data Analysis Code:** The code used to replicate the analysis in this paper can be found [here](https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html).
+ **Study Applet:** The shiny app used to conduct the study can be accessed [here](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/).
+ **\ear{RShiny Applet Code:}** \ear{The code used to create the RShiny Applet for data collection can be found} [\ear{here}](https://github.com/earobinson95/you-draw-it-validation-applet).

### 2022-01-28 Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
updated shinyapps.io link to new repository rsconnect

Participants were recruited through through Twitter, Reddit, and direct
email in May 2021. A total of 35 individuals completed 119 unique `You
Draw It' task plots; all completed you draw it task plots were included
in the analysis. All participants had normal or corrected to normal
vision and signed an informed consent form. The experimental tasks took
approximately 15 minutes to complete. While this study does utilize a
convenience sample, as this is primarily a perceptual task, previous
results have found few differences between expert and non-expert
participants in this context \citep{vanderplas2015spatial}. These data
were collected to validate this method of graphical testing, with the
hopes of providing a new tool to assess graphical perception
interactively. Participants completed the experiment on their own
computers in an environment of their choosing. The experiment was
conducted and distributed through a Shiny application \citep{shinyPkg}
{\textcolor{blue}{xxx added citation}} found
\href{https://emily-robinson.shinyapps.io/you-draw-it-pilot-app/}{here}.
{\textcolor{RedOrange}{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?}}
{\textcolor{blue}{XXX currently linked to my shinyapps.io page but will get this updated to a new repository.}}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available to be downloaded from
  GitHub
  \href{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}{here}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be found
  \href{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}{here}.
\item
  \textbf{Study Applet:} The shiny app used to conduct the study can be
  accessed
  \href{https://emily-robinson.shinyapps.io/you-draw-it-pilot-app/}{here}.
\item
  \textbf{{\textcolor{blue}{RShiny Applet Code:}}}
  {\textcolor{blue}{The code used to create the RShiny Applet for data collection can be found}}
  \href{https://github.com/earobinson95/you-draw-it-validation-applet}{{\textcolor{blue}{here}}}.
\end{itemize}

>>>>

Participants were recruited through through Twitter, Reddit, and direct
email in May 2021. A total of 35 individuals completed 119 unique `You
Draw It' task plots; all completed you draw it task plots were included
in the analysis. All participants had normal or corrected to normal
vision and signed an informed consent form. The experimental tasks took
approximately 15 minutes to complete. While this study does utilize a
convenience sample, as this is primarily a perceptual task, previous
results have found few differences between expert and non-expert
participants in this context \citep{vanderplas2015spatial}. These data
were collected to validate this method of graphical testing, with the
hopes of providing a new tool to assess graphical perception
interactively. Participants completed the experiment on their own
computers in an environment of their choosing. The experiment was
conducted and distributed through a Shiny application \citep{shinyPkg}
{\textcolor{blue}{xxx added citation}} found
\href{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}{here}.
{\textcolor{RedOrange}{We should probably make a rstudioconnect version that saves data to e.g. a google spreadsheet? Just in case my server goes down or something?}}
{\textcolor{blue}{XXX linked to updated shinyapps.io through new repository - does not currently write data anywhere.}}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses are available to be downloaded from
  GitHub
  \href{https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data}{here}.
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper can be found
  \href{https://earobinson95.github.io/Eye-Fitting-Straight-Lines-in-the-Modern-Era/analysis/you-draw-it-eyefitting-analysis.html}{here}.
\item
  \textbf{Study Applet:} The shiny app used to conduct the study can be
  accessed
  \href{https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/}{here}.
\item
  \textbf{{\textcolor{blue}{RShiny Applet Code:}}}
  {\textcolor{blue}{The code used to create the RShiny Applet for data collection can be found}}
  \href{https://github.com/earobinson95/you-draw-it-validation-applet}{{\textcolor{blue}{here}}}.
\end{itemize}
